Bulk Semantic Annotation with a Partially Known Knowledge Base

### 2024-12-08 doc/cicm25-sysdesc/sysdesc.tex
draining

In fully formal authoring e.g. for programming, the content commons is given formally in
the form of the libraries of the respective programming language, correspondingly the
authored content is also formal -- a program -- and intended for processing by a computer,
for which the formality is a prerequisite.

@@

The current interface is not well-suited for on-the-fly annotation while authoring.
For that, the underlying information (the symbol/verbalization pairs harvested
from the domain model) can be integrated into any IDE. In fact we plan to do this for the
next version of the sTeX plugin for VSCode \cite{sTeX-IDE:git}.

@@

In this system description we have presented \snify, a command-line tool
\ednote{continue} \snify is open source;
the source and documentation are available from \cite{stextools:git}.

>>>>

In fully formal authoring e.g. for programming, the content commons is given formally in
the form of the libraries of the respective programming language, correspondingly the
authored content is also formal -- a program -- and intended for processing by a computer,
for which the formality is a prerequisite. Formal authoring is usually supported by an
integraded development environment (IDE) that makes use of the fully formal content and
offers services like semantic tab completion

@@

One practical problem with \snify that remains is that the system only harvests
symbol/verbalization pairs from \sTeX files on the local file system. This means that for
effective annotation users (have to) download the whole content commons and keep it
updated. Unfortunately, the current MMT-based MathHub knowledge management
API\ednote{intro this above} does not supply verbalization information. The iMMT-based
API~\cite{iMMT:on} currently under development will, so \snify will be able to request the
pairs for the remaining (non-local) content commons. If a pair is chosen in an annotation,
\snify can then automatically download the corresponding archive so that the annotated
file can be formattted with pdflatex or rusTeX locally.

Finally, the current interface is not well-suited for on-the-fly annotation while
authoring.  For that, the underlying information (the symbol/verbalization pairs harvested
from the domain model) can be integrated into any IDE. In fact we plan to do this for the
next version of the sTeX plugin for VSCode \cite{sTeX-IDE:git}.

@@

In this paper we have presented the semantic authoring problem using the \sTeX corpus and
the adaptive learning assistant \ALeA as a concrete example. We have shown that it differs
from both classical authoring and formal authoring in terms of the necesssary system
support. As an example of specialized authoring support, we have presented \snify, a
command-line tool that bridges the gap between formal symbols in \sTeX and

\snify is open source; the source and documentation are available from
\cite{stextools:git}.
